\documentclass[margin,line]{res}
\usepackage{hyperref}
\usepackage{enumitem}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}
\name{Qi (Rose) Yu\vspace*{.1in}}
\begin{resume}
\section{\sc }
\vspace{.05in}
\begin{tabular}{@{}p{3.5in}p{4in}}
9500 Gilman Drive, Mail Code 0404
 & {\it E-mail:}  \url{roseyu@ucsd.edu } \\   
Department of Computer Science and Engineering \\University of California, San Diego & {\it Phone:}  (858) 246-4724 \\            
La Jolla, CA 92093-0404   & {\it Homepage:} \url{http://roseyu.com} \\     
\end{tabular}


\section{\sc Research}
Large-Scale Spatiotemporal  Learning, Deep Learning, Tensor Methods, and their applications.

\section{\sc Current Appointment}


{\bf University of California, San Diego}, La Jolla, California \\
{\em Assistant Professor}, {\em Department of Computer Science and Engineering}  \hfill {July 2020 - Present }
%\vspace*{-.1in}
%\begin{list1}
%	\item[] Assistant Professor,  Aug 2018 - Present 
%    %Adjunct Assistant Professor, Aug 2017 - Aug 2018  
%	\vspace*{.05in}
%\end{list1}


\section{\sc Previous Appointment}

{\bf Northeastern University}, Boston, Massachusetts \\
{\em Assistant Professor}, {\em Khoury College of Computer Sciences}  \hfill {Aug 2018 - June 2020 }\\
{\em Network Science Institute, College of Engineering, Physics (By Courtesy)}


{\bf California Institute of Technology}, Pasadena, California\\
{\em Postdoctoral Scholar,  Computing + Mathematical Sciences} \hfill {Aug 2017 - Aug 2018}

\begin{list2}
\item Advisors:  Anima Anandkumar, Yisong Yue
\end{list2}
%\vspace*{-.1in}
%\begin{list1}
%	\item[] Postdoctoral Scholar,  Aug 2017 - Aug 2018
%%	\item[]  08/21/2017 - present
%	\begin{list2}
%		\vspace*{.05in}
%		\item Advisors:  Anima Anandkumar, Yisong Yue
%	\end{list2}
%	\vspace*{.05in}
%\end{list1}


{\bf Stanford University}, Palo Alto, California\\
{\em Visiting Researcher,  Computer Science Department} \hfill { Aug 2016 - Oct 2016}

\begin{list2}
\item Host:  Christopher R\'e
\end{list2}

{\bf  IBM  Research}, Yorktown Heights, New York\\
\vspace{-.2cm}
{\em Research Intern} \hfill {June 2015 - Aug 2015}
%Work with Hongfei Li, Anshul Sheopuri in Customer Analytic team on IBM Xtify push intelligence platform. Developed deep learning models for GPS data from Xtify to predict users' click behavior and build customer profiles. 


{\bf  Yahoo! Labs}, Sunnyvale, California\\
\vspace{-.2cm}
{\em Research Intern} \hfill { June 2014 - Aug 2014} 
%Work with Andrew Gelfand, Suju Rajan in Personalization team on Yahoo! Aviate location-aware app recommendation. Developed a hierarchical Bayesian model for geographical segmentation problem in App usage. Continue academic collaboration through November on ``Geographic Segmentation via Latent Poisson Factor Model".
%


{\bf  Intel Lab}, Santa Clara, California\\
\vspace{-.2cm}
{\em Research Intern} \hfill{May 2013 - Aug 2013}
%Work with Context-Aware Technology team of Intel Immersive Experience Research (IXR) division. 
%Analyze smart phone usage data and propose a graphical model based algorithm to predict the potential contacts and applications on smart phones.
%Analyze NBC Universal movie data and fit regression models to predict future DVD/CD sales.

{\bf  Microsoft R\&D}, Minghang, Shanghai\\
\vspace{-.2cm}
{\em Program Manager Intern} \hfill {June  2011 - June  2012}
% Work with Commerce team in Microsoft’s Server \& Tools Business.
% Build SDK Wiki for Commerce platform partners.  
% Design API prototype for guest purchase without Window Live ID authentication feature.
%Adapt platform working flow of payment instruments risk check and fraud detection for Microsoft Office 360 and Azure.

\section{\sc Education}
{\bf University of Southern California}, Los Angeles, California\\
{\em Ph.D., Computer Science, Computer Science Department} \hfill {Aug 2012 - Aug 2017}\\
{\em Thesis: Tensor Learning for Large-Scale Spatiotemporal Analysis} \\
{\em Finalist in William F. Ballhaus, Jr. Prize for Excellence in Graduate Engineering Research}
%\item[] Research Assistant, 08/20/2012 - 08/08/2017
\begin{list2}
\vspace*{.05in}
\item Advisors:  Yan Liu, Cyrus Shahabi
\end{list2}


%{\bf Stanford University}, Stanford, California\\
%{\em Computer Science Department } 
%%\vspace*{-.1in}
%\begin{list1}
%	\item[] Visiting Student Researcher, Aug 2016 - Oct 2016
%	%\item[] Aug 2016 - Oct 2016
%	\begin{list2}
%		\vspace*{.05in}
%		\item Host:  Christopher R\'e
%	\end{list2}
%\end{list1}

{\bf Zhejiang University}, Hangzhou, Zhejiang, PRC\\
{\em B.S in Computer Science, Chu Kochen Honors College} \hfill {Aug 2008 - June 2012}
%\vspace*{-.1in}
\begin{list2}
\vspace*{.05in}
\item Advisor:  Zhihua Zhang
\end{list2}

% {\bf University of California, Davis}, Davis, California, USA\\
% %{\em Department of Mathematics and Statistics} 
% \vspace*{-.1in}
% \begin{list1}
% \item[]  Exchange Student, Jan 2010-Feb 2010
% \end{list1}


\section{\sc Selected Awards and Honors} 

%WSDM SIGIR Travel Grant, San Fransisco, CA, 2016
\textbf{AWS Machine Learning Research Awards},  Amazon Science, 2020

\textbf{Adobe Data Science Research Awards},  Adobe Research, 2020

\textbf{Google Faculty Research  Award},  Google Research, 2019-2020

\textbf{Best Paper Award},  NeurIPS Machine Learning for Public Health, 2020


\textbf{Best Dissertation Award}, University of Southern California, 2018

\textbf{Best Paper Award},  NIPS Time Series Workshop, 2017

\textbf{SIGKDD Scholarship},  ACM 50th Celebration of the Turing Award, San Francisco, 2017

\textbf{Rising Stars in EECS},  40 Awardees in North America, MIT, 2015

\textbf{Annenberg Graduate Fellowship}, University of Southern California, 2012

%Graduate School Ph.D. Fellowships Travel Award, Univesity of Southern Califonia, 2015


%USC Annenberg Graduate Fellowship Research  Creative  Symposium Award, University  of Southern California, 2015


%WiSE Travel Grant for Graduate Students and Post-doctoral Fellows, Montreal, CA,2014


%NIPS 2014 Conference Travel Award, Montreal, CA,2014
%
%2014 Broadening Participation in Data Mining Travel Scholarship,New York, US, 2014 

\textbf{Selected in ACM Heidelberg Laureate Forum }, University of Heidelberg, 2013

%Excellent university graduate in Zhejiang Province,  Department of Education of Zhejiang Province, 2012
%GHC scholarship, The Grace Hopper Celebration of Women in Computing, 2012

\textbf{Microsoft 2011 Young Fellowship}, Microsoft Research Asia, 2011

%AAAI 2011 Conference Student Scholarship, AAAI, 2011 

\textbf{International Forum (iF) Design Hanover Global Concept Award}, iF, 2010 

\textbf{First prize in Undergraduate Research and Innovation}, Zhejiang University, 2010   

%\textbf{Outstanding Undergraduate Award}, Zhejiang University, 2009, 2008. 




%\section{\sc Preprints}
%\begin{enumerate}[label={[P\arabic*]}]
%\item Ruichao Xiao, \underline{Rose Yu}
%"Dynamic Relational Inference in Multi-Agent Trajectories"
%Preprint \textit{arXiv:2007.13524}
%
%
%     
%\item Rui Wang, Robin Walters, \underline{Rose Yu}
%"Incorporating Symmetry into Deep Dynamics Models for Improved Generalization"
%Preprint \textit{arXiv:2002.03061}
%
%
%\item \underline{Rose Yu}, Sung-En Chang, Xun Zheng, Ian E.H. Yen, Pradeep Ravikumar
%"Efficient Tensor Decomposition with Boolean Factors"
%Preprint \textit{arXiv:1810.04754}
%	
%%\item  Stephan Zheng, \underline{Rose Yu}, Yisong Yue
%%	"Multi-resolution Tensor Learning for Large-Scale Spatial Data"
%%	Preprint \textit{arXiv:1802.06825}
%	
%\item \underline{Rose Yu,} Stephan Zheng, Anima Anandkumar, Yisong Yue
%"Long-term Forecasting using Tensor-Train RNNs"
%Preprint \textit{arXiv:1711.00073}
%
%
%\item Paroma Varma, Bryan He, Dan Iter, Peng Xu,  \underline{Rose Yu}, Christopher De Sa,  Christopher R\'e,  "Socratic Learning",
%Preprint \textit{arXiv:1610.08123}
%\end{enumerate}


\section{\sc Conference Publications}

%\subsection{\sc Conferences}
\begin{enumerate}[label={[C\arabic*]}]
\item  Robin Walters, Jinxi (Leo) Li, \underline{Rose Yu} "Trajectory Prediction using Equivariant Continuous Convolution", To appear in  \textit{International Conference on Learning Representations} (ICLR), 2021

\item  Rui Wang, Robin Walters, \underline{Rose Yu} "Incorporating Symmetry into Deep Dynamics Models for Improved Generalization", To appear in  \textit{International Conference on Learning Representations} (ICLR), 2021

\item Fan Xie,  Alex  Chowdhury, Clara De Paolis, Linfeng Zhao, Lawson Wong,  \underline{Rose Yu}
"Deep Imitation Learning for Bimanual  Robotic Manipulation"
  In Proceeding of \textit{Advances in Neural Information Processing Systems} (NeurIPS), 2020
  
\item Armand Comas Massague, Chi Zhang, Zlatan Feric, Octavia Camps,  \underline{Rose Yu}
"Learning Disentangled Representations of Video with Missing Data"
  In  Proceeding of \textit{Advances in Neural Information Processing Systems} (NeurIPS), 2020
 
 
\item Chintan Shah, Nima Dehmamy, Nicola Perra, Matteo Chinazzi, Albert-László Barabási, Alessandro Vespignani, \underline{Rose Yu}
"Finding Patient Zero: Learning Contagion Source with Graph Neural Networks"
 In \textit{International Conference on Network Science} (NetSci),  2020. 
     
 \item Csaba Both, Nima Dehmamy,  Albert-László Barabási, \underline{Rose Yu}
"Network Layout using Graph Neural Networks"
 In \textit{International Conference on Network Science} (NetSci),  2020.  
      
\item Jung Yeon Park, Kenneth Theo Carr, Stephan Zheng, Yisong Yue, \underline{Rose Yu}
"Multiresolution Tensor Learning for Efficient and Interpretable Spatial Analysis"
 In Proceedings  of  \textit{the 32th International Conference on Machine Learning} (ICML), 2020

\item Rui Wang, Adrian Albert,  Karthik, Kashinath, Mustafa, Mustafa,  \underline{Rose Yu}. "Towards Physics-informed Deep Learning for Spatiotemporal Modeling of Turbulent Flows", In  Proceeding of\textit{ ACM SIGKDD Conference on Knowledge Discovery and Data Mining} (KDD), 2020

\item Eliza Huang, Rui Wang, Uma Chandrasekaran, \underline{Rose Yu}.  "Aortic Pressure Forecasting with Deep Sequence Learning", In  Proceeding of  \textit{Computing in Cardiology} (CinC), 2020 

\item Nima Dehmamy, Albert-L\'aszl\'o Barab\'asi, \underline{Rose Yu}.  "Understanding the Representation Power of Graph Neural Networks in Learning Graph Topology" In Proceeding of  \textit{Advances in Neural Information Processing Systems} (NeurIPS), 2019
 
 
\item  Yukai Liu, \underline{Rose Yu}, Stephan Zheng, Eric Zhan, Yisong Yue. "NAOMI: Non-Autoregressive Multiresolution Sequence Imputation" In  Proceeding of  \textit{Advances in Neural Information Processing Systems} (NeurIPS), 2019


\item Guanya Shi, Xichen Shi, Michael O'Connell, \underline{Rose Yu}, Kamyar Azizzadenesheli, Anima Anandkumar, Yisong Yue, Soon-Jo Chung. "Neural Lander: Stable Drone Landing Control using Learned Dynamics" In  Proceedings  of \textit{ International Conference on Robotics and Automation} (ICRA), 2019

\item 	Yaguang Li,  \underline{Rose Yu}, Cyrus Shahabi, Yan Liu. "Diffusion Convolutional Recurrent Neural Network: Data-Driven Traffic Forecasting" In  Proceedings  of   \textit{International Conference on Learning Representations}(ICLR), 2018 
	
\item  \underline{Rose Yu}, Guangyu Li, Yan Liu. "Tensor regression meets Gaussian Processes." In Proceedings  of   \textit{International Conference on Artificial Intelligence and Statistics} (AISTATS), 2018 

\item \underline{Rose Yu}, Yaguang Li, Ugur Demiryurek, Cyrus Shahabi, Yan Liu. "Deep Learning: A Generic Approach for Extreme Condition Traffic Forecasting." In   Proceedings  of  \textit{the Seventeenth SIAM International Conference on Data Mining }(SDM), 2017

\item \underline{Rose Yu}, Yan Liu. "Learning from Multiway Data: Simple and Efficient Tensor Regression." In Proceedings  of  \textit{International Conference on Machine Learning }(ICML),   2016

\item Dingxiong Deng, Cyrus Shahabi, Ugur Demiryurek, Linhong Zhu,  \underline{Rose Yu}, Yan Liu, 
"Latent Space Model for Road Networks to Predict Time-Varying Traffic", In Proceeding of  \textit{ACM SIGKDD Conference on Knowledge Discovery and Data Mining } (KDD), 2016


\item \underline{Rose Yu}, Andrew Gelfand, Suju Rajan, Cyrus Shahabi, Yan Liu. "Geographic Segmentation via Latent Poisson Factor Model." In \textit{ACM International Conference on Web Search and Data Mining} (WSDM), 2016 

\item \underline{Rose Yu}, Dehua Cheng, Yan Liu. "Accelerated Online Low Rank Tensor Learning for Multivariate Spatiotemporal Streams." In Proceedings  of  \textit{International Conference on Machine Learning} (ICML), 2015

\item \underline{Rose Yu}, Mohammad Taha Bahadori, Yan Liu. "Fast Multivariate Spatio-temporal Analysis via Low Rank Tensor Learning." In Proceeding of  \textit{Advances in Neural Information Processing Systems} (NIPS), 2014 \textbf{Spotlight}

\item \underline{Rose Yu}, Xinran He, Yan Liu. "GLAD: Group Anomaly Detection in Social Media Analysis." In Proceeding of  \textit{ACM SIGKDD Conference on Knowledge Discovery and Data Mining} (KDD), 2014

\item Cuixia Gao, Naiyan Wang,\underline{Qi Yu}, Zhihua Zhang. "A Feasible Nonconvex Relaxation Approach to Feature Selection." In \textit{Proceeding of 24th AAAI Conference on Artificial Intelligence} (AAAI), 2011 

%\item  \underline{Qi Yu}, Zhihao Ding, Rong Rong, Wang Donghui, Zhengyue Zhang. "Dark Pixel Detection: A Novel Single Image Dehaze Approach". In \textit{Proceeding of 27th Image and Vision Computing New Zealand }(IVCNZ), 2011  
\end{enumerate}

 
\section{\sc Journal Publications}
\begin{enumerate}[label={[J\arabic*]}]
\item K. Kashinath, M. Mustafa, A. Albert,J-L. Wu, C. Jiang, S. Esmaeilzadeh ,K. Azizzadenesheli, R. Wang, A.Singh, A. Manepalli, D. Chirila, \underline{R.Yu}, R. Walters, B. White, H. Xiao, H. A. Tchelepi, P. Marcus, A. Anandkumar,  Prabhat. "Physics-informed machine learning: Case studies for weather and climate modelling" In \textit{Journal of Philosophical Transactions of the Royal Society  A}, 2020

\item \underline{Rose Yu}, Stephan Zheng, Anima Anandkumar, Yisong Yue. "Long Term Forecasting with Higher Order Tensor RNN". In  \textit{ Journal of Machine Learning Research} (JMLR), 2018



\item \underline{Rose Yu},  Yan Liu.  "Spatio-Temporal Analysis of Social Media Data"  In \textit{Encyclopedia of GIS}, 2016

\item \underline{Rose Yu}, Huida Qiu, Zhen Wen, Ching-Yung Liu,  Yan Liu. "A Survey on Social Media Analysis  Anomaly Detection" In \textit{ACM KDD Exploration},  2016

\item \underline{Rose Yu}, Xinran He, Yan Liu. "GLAD: Group Anomaly Detection in Social Media Analysis - Extended Abstract." In \textit{}ACM Transactions on Knowledge Discovery in Data  (TKDD), 2015
\end{enumerate}

\section{\sc Selected
Workshop
Papers
(Unrefereed) }
\begin{enumerate}[label={[W\arabic*]}]

\item Rui Wang, Danielle Maddix,Christos Faloutsos, Yuyang Wang, \underline{Rose Yu}. "Physics-based vs. Data-driven: A Benchmark Study on COVID-19 Forecasting",  \textbf{Best Paper Award}  in \textit{Advances in Neural Information Processing Systems} (NeurIPS), Machine Learning for Public Health workshop, 2020



\item Rui Wang, Adrian Albert, Karthik Kashinath, Mustafa Mustafa, \underline{Rose Yu}. "Towards physics informed deep learning for spatiotemporal modeling of turbulence flow". \textbf{Oral Presentation} at \textit{Advances in Neural Information Processing Systems} (NeurIPS), Machine Learning for Physical Sciences  workshop, 2019

\item Clara De Paolis, Saeed Amizadeh, \underline{Rose Yu}.  "A Neural Framework for Learning DAG to DAG Translation ". In  \textit{Advances in Neural Information Processing Systems} (NeurIPS), relational representation learning workshop, 2018

\item \underline{Rose Yu}, Stephan Zheng, Anima Anandkumar, Yisong Yue. "Long-term forecasting using Tensor-Train RNN". \textbf{Best Paper Award}  in \textit{Advances in Neural Information Processing Systems} (NIPS), time series workshop, 2017


\item Yaguang Li, \underline{Rose Yu}, Cyrus Shahabi, Yan Liu. "Diffusion Convolutional Recurrent Neural Network: Data-Driven Traffic Forecasting". \textbf{Oral Presentation} at \textit{Advances in Neural Information Processing Systems} (NIPS), time series workshop, 2017


\item \underline{Rose Yu}, Stephan Zheng. "Learning Chaotic Dynamics with Tensor RNN". In  \textit{International Conference on Machine Learning} (ICML), Deep structured prediction workshop, 2017

\item \underline{Rose Yu},  Paroma Varma, Dan Iter, Chris De Sa, Christopher Re,  "Socratic Learning".  In \textit{Advances in Neural Information Processing Systems}  (NIPS) future of interactive machine learning workshop, 2016

%
%\item Rose Yu, Yan Liu. "Simple and Efficient Tensor Regression for Spatio-Temporal Forecasting." Poster accepted to \textit{International Workshop on Climate Informatics workshop}(CI), 2016
%
%\item Rose Yu, Dehua Cheng, Yan Liu. "Accelerated Online Low-Rank Tensor Learning for Multi-model Ensemble." Poster accepted to \textit{International Workshop on Climate Informatics workshop} (CI), 2015
%
%\item Mohammad Taha Bahadori, Rose Yu, Yan Liu. "Fast Cokriging via Low Rank Tensor Learning." Poster accepted to \textit{International Workshop on Climate Informatics workshop} (CI), 2014
\end{enumerate}


\section{\sc Awarded Grants}
\begin{enumerate}[label={[G\arabic*]}]
\item PI, {Abiomed Research Grant},, \textit{Automated Patient Care Assistant via Machine Learning}, \$299,480, Nov 2020 - Oct 2023.
\item PI,   Army Research Office,  \textit{W911NF-20-1-0334: Physics-Guided Learning for Sample Efficient Spatiotemporal Decision Making}, \$370,704, Sep 2020 - Aug 2023. 
\item Co-PI, DARPA SBIR, \textit{W31P4Q-21-C-0014: Combining Simulated and Real Data
for Near-Term Forecasting of Nonstationary Dynamic Processes}, July 2020 - Dec 2020.
\item PI,  ALCF Director’s Discretionary (DD) Program Allocation Award \textit{Graph Neural Networks},  2 million core hours, June 2020 - Jan 2021.
\item PI,  NERSC AY 2020 Exploratory Allocation Award \textit{Physcis Informed Deep Learning for Predicting Turbulence Flow}, 45,000  (NERSC MPP Hours) , Jan 2020 - Jan, 2021.
\item  PI, {NSF CRII},    \textit{IIS-1850349/2037745: Multiresolution Tensor Learning for Scalable and Interpretable Spatiotemporal Analysis},    \$174,998,  Aug, 2019 - July, 2021

\item PI, {Abiomed Research Grant},    \textit{Anticipating Patient Outcome via Machine Learning}, \$50,000, July, 2019 - Sep, 2020

\item PI,  {ONR STTR}, \textit{N68335-19-C-0310: Subcontract: Predictive Graph Convolutional Networks},  \$71,784, June, 2019 - Dec, 2019


\item Co-PI,  {Mathworks Microgrant},    \textit{Battery State of Health Machine Learning Prognostics}, \$17,400,  Sep, 2019 - Dec, 2019
 
\item Co-PI,  {ONR ECP}, \textit{Subcontract: Learning and Prediction of Dynamic Processes on Evolving Networks}, \$28,840,  March, 2019 - Oct, 2019	

\item PI,  Northeastern Tier 1, \textit{Physics-Informed Deep Learning for High-Resolution Climate Extremes Modeling}, \$50,000, July, 2019 - Sep, 2020

\item PI, Northeastern Khory Seed Grant, \textit{Learning Bimanual Robotic Manipulation Via Deep Graph Sequence }, \$50,000,  Aug, 2019 - Aug, 2020	

\item NVIDIA GPU Grant Oct 2018, 1  Titan Xp,  Amazon AWS Research Credits, Oct  2018, \$20,000 Cloud Credits, Google Cloud Research Credits, Oct, 2018, \$10,000 Cloud Credits

\end{enumerate} 



\section{\sc Advising }
{\bf Postdocs Supervised} \\


\begin{list2}
\item Robin Walters, 2020, active 
\end{list2}




{\bf Ph.D. Students Advised} \\

\begin{list2}
\item Weitang Liu, 2020, active
\item Rui (Ray) Wang, 2019, active 
\item Jung Yeon (John) Park, 2019 - 2020,  advised at Northeastern
\item Clara De Paolis, 2018 -2020,  advised at Northeastern
\end{list2}


 

\section{\sc Teaching }
 {\bf Deep Generative Models  (CSE 291(G00) )}   \hfill  {Fall 2020} 



 {\bf Advanced Machine Learning  (CS 7140)}   \hfill  { Spring 2020} 


 {\bf Machine Learning Seminar (CS 4950)}   \hfill  { Fall 2019} 

 {\bf Introduction to Computer Science Research (CS 3950)}   \hfill  { Fall 2019} 
 
 {\bf Special Topics in AI: Deep Learning (CS 7180)}   \hfill  { Spring 2019} 


 {\bf Machine Learning (CS 6140)}   \hfill  { Fall 2018 } 


% {\bf Machine Learning (CSCI 567)}   \hfill  { Spring 2016 } 
% 
% \vspace{-.3cm}
% Guest  lecturer : taught Gaussian mixture models and EM algorithm.
 
% 
% {\bf Advanced Big Data Analytics (CSCI 686)}   \hfill  {Fall 2015} 
% 
% \vspace{-.3cm}
%Teaching assistant: Led weekly section; redesigned assignments and mini-project on topic modeling to reflect developments in big data analysis. 

%\section{\sc Invited Talks}
%2015 Convolutional Wasserstein Distances for Geometry Processing
%Geometry Workshop, Seggau, Austria
% \section{\sc Research Grant}
% \begin{enumerate}[label={[G\arabic*]}]
% \item Mathworks Microgrant, \textit{Battery State of Health Machine Learning Prognostics}, Feb 2019, \$17,400 (50\%)

% \item Abiomed, \textit{Anticipating Patient Outcomes via Machine Learning}, Feb 2019, \$50,000 

% \item NSF, \textit{CRII: III: Multiresolution Tensor Learning for Scalable and Interpretable Spatiotemporal Analysis} Recommended for Award,  Dec 2018, \$174,998


% \end{enumerate}



\section{\sc Invited Talk}
 {\bf Year  2021}

Oak Ridge National Laboratory Workshop on AI for Robust Engineering \& Science \hfill{Jan 2020}

 {\bf Year  2020}

NeurIPS 2020 Workshop on Quantum Tensor Networks \hfill{Dec 2020}

NeurIPS 2020 Workshop on AI for Earth \hfill{Dec 2020}

NeurIPS 2020 Workshop on Interpretable Inductive Biases \hfill{Dec 2020}

AGU Fall Meeting Invited Talks \hfill{Dec 2020}

AAAI 2020 Symposium on Physics-Guided AI for Accelerating Scientific Discovery \hfill{Nov 2020}

LA Life Science Summit \hfill{Oct 2020}

COVID-19 Forecast Hub  \hfill{Sep 2020}
 
International School and Conference on Network Science  \hfill{Sep 2020}
 
 
 ODSC Europe 2020 Virtual Conference \hfill{Sep 2020}

 
 Mathematics of Data Science Virtual Lecture Series, Tufts, MA \hfill{June 2020}
 
 
Facebook Artificial Intelligence Research,  Menlo Park, CA \hfill{April 2020}


 Functional Data over Multidimensional Domain, EPFL, Switzerland,   \hfill{April 2020}
 
 
AI for Robust Engineering and Science workshop,  Oak Ridge National Lab \hfill{Jan 2020}
 
 
Physics Informed Machine Learning workshop,  Los Alamos National Lab \hfill {Jan 2020}


 {\bf Year  2019}
 

Mitsubishi Electric Research Laboratories (MERL), Cambridge  \hfill {Oct  2019}


\textbf{Plenary Speaker},  European Research Network on System Identification   \hfill {Sep, 2019}


Hazy Research Group Seminar,  Stanford University  \hfill {August 2019}

KDD 2019 Tensor Methods Workshop, Anchorage \hfill{August 2019}

University  of Connecticut,   Connecticut \hfill{July 2019}

Google  Research, Mountain View \hfill{July 2019}

Machine Learning Theory Workshop,  Peking University, China  \hfill{June 2019}

Auto Lab, University of Michigan, Ann Arbor  \hfill{May 2019}

ICLR 2019 Workshop on Deep Generative Models, New Orleans  \hfill{May 2019}

Tensor Working Group  on Simons Foundation, New York  \hfill{May  2019}

Workshop Low-rank Optimization and Applications,  Leipzig, Germany \hfill{April 2019}

 Young European Probablists XV workshop, Eindhoven, Netherland  \hfill{March 2019}
 
 Lawrence Berkeley National Laboratory (LBNL) \hfill{March 2019}

 {\bf Year  2018}
 
Amazon Research, Palo Alto \hfill{Dec 2018}

Salesforce Research, Palo Alto, \hfill{Dec 2018}

Machine Learning Group Seminar, Harvard, \hfill {Nov 28 2018} 

Clinical Machine Learning Group Seminar, MIT, \hfill {Nov 13  2018} 


\textbf{Keynote Speaker},  Climate Informatics 2018 (CI 2018), \hfill {Sep 2018} 


Henry L. Pierce Laboratory Seminar Series, MIT, \hfill {Sep 12, 2018}

Japan RIKEN  Center for Advanced Intelligence Project (AIP), Tokyo, \hfill {July 3, 2018}

Disney Research, Burbank, \hfill {May 22, 2018}

 {\bf Year  2017}
 
Department of Management Science,  University of Miami  \hfill {Nov 18, 2017}


Department of Computing and Mathematically Sciences,  Caltech  \hfill {Oct 6, 2017}


Center of Data Science, New York University  \hfill {March 30, 2017}


Department of Computer Science, Brown University   \hfill {March 13, 2017}



School of Industrial and Systems Engineering, Georgia Institute of Technology  \hfill {March 6, 2017}


College of Computer and Information Science, Northeastern University  \hfill {March 3, 2017}


 
 AI with The Best, Online Conference \hfill {Sep 17, 2016}
 
 
Computer Science Department,  Stanford University  \hfill {May 23, 2016}
 
 
%Department of  Electrical \& Computer Engineering,  Northeastern University  \hfill {Nov 12, 2015}


\section{\sc Academic Service}
{\bf Workshop Co-organizer}

NeurIPS  Workshop on Machine Learning for Engineering, 2020\\
ICML Time Series  Workshop, 2019 \\
ICML Time Series  Workshop, 2017 \\
NIPS Woman in Machine Learning Workshop, 2016 \\
NIPS workshop on Learning with Tensors: Why Now and How? (Tensor-Learn), 2016 \\



{\bf Conference Organizing Committee}

Poster Chair, KDD (2020) \\
Proceedings Chair, SIGSPATIAL (2020) \\
KITP: At the Crossroad of Physics and Machine Learning,  2019\\
Proceedings Chair, WSDM (2018)\\
Short Paper Chair, CIKM (2017)

{\bf Grant Reviewer/Panelist}

 Department of Energy (DOE) Review Panel, 2019, 2020 \\
National Science Foundation (NSF) Review Panel, 2018, 2019



{\bf Senior Program Committee (or Area Chair)}

 ICML(2021, 2020), ICLR (2021), NeurIPS (2020), AAAI (2021), IJCAI (2020), SDM (2020)

{\bf Program Committee}

ICML (2020, 2019, 2018), NeurIPS (2019, 2018), ICLR (2020, 2019), KDD (2019), AISTATS (2020, 2019), SDM (2019), AAAI (2018), IJCAI (2018), CIKM (2017), NIPS Time Series Workshop (2016), ICML Time Series Workshop (2016) 


{\bf Reviewer}

Proceedings of IEEE (2019), Journal of Machine Learning Research (JMLR), Journal of Artificial Intelligence Research (JAIR), Transactions on Knowledge Discovery from Data (TKDD), IEEE Transactions on Knowledge and Data Engineering (TKDE),  IEEE Intelligent Transportation Systems Transaction (ITS)


%Co-organizer, USC PhD Woman in Computer Science group, Los Angeles, 2013
%Conference Volunteer, 24th AAAI conference on Artificial Intelligence, San Francisco, 2011

%Student Local Chair, ACM Conference on Computer Supported Cooperative Work (CSCW), Hangzhou, 2011

%Organizer, Probabilistic Intelligence Lab Machine Learning Seminar, Hangzhou, 2010
%
%President, Chu KoChen Honors College Excellent Student League, Hangzhou, 2009


%
%\section{\sc Computer Skills} 
%\begin{list2}
%\item Languages:  C/C++/C\#, Python, Java,  MATLAB script, R, SQL, Unix shell scripts.
%
%\item Softwares:  Eclipse, Android Studio, Visual Studio, R Studio, MATLAB, Hadoop/Hive, MySQL, \LaTeX , Vim, Microsoft Office.
%
%%\item Algorithms: Variational Bayes and Markov Chain Monte Carlo simulations of Bayesian posterior distributions
%
%\item Operating Systems:  Unix/Linux, Windows.\\ 
%\end{list2}



\end{resume}
\end{document}




