\documentclass[margin,line]{res}

\usepackage{hyperref}
\usepackage{enumitem}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}
\name{Qi (Rose) Yu\vspace*{.1in}}
\begin{resume}
\section{\sc }
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
177 Huntington Ave Office 921 & {\it E-mail:}  \url{roseyu@northeastern.edu } \\   
Northeastern University & {\it Phone:}  (617) 373-6455 \\            
Boston, MA 02115 USA    & {\it Homepage:} \url{http://roseyu.com} \\     
\end{tabular}


\

\section{\sc Preprints}
\begin{enumerate}[label={[P\arabic*]}]

\item Rui Wang, Adrian Albert, Karthik Kashinath, Mustafa Mustafa, \underline{Rose Yu}. "Towards physics informed deep learning for spatiotemporal modeling of turbulence flow".       Preprint \textit{arXiv:1911.08655}

\item \underline{Rose Yu}, Sung-En Chang, Xun Zheng, Ian E.H. Yen ,Pradeep Ravikumar
      "Efficient Tensor Decomposition with Boolean Factors"
      Preprint \textit{arXiv:1810.04754}
	
\item  Stephan Zheng, \underline{Rose Yu}, Yisong Yue
	"Multi-resolution Tensor Learning for Large-Scale Spatial Data"
	Preprint \textit{arXiv:1802.06825}
	
\item \underline{Rose Yu,} Stephan Zheng, Anima Anandkumar, Yisong Yue
"Long-term Forecasting using Tensor-Train RNNs"
Preprint \textit{arXiv:1711.00073}


\item Paroma Varma, Bryan He, Dan Iter, Peng Xu,  \underline{Rose Yu}, Christopher De Sa,  Christopher R\'e,  "Socratic Learning",
Preprint \textit{arXiv:1610.08123}
\end{enumerate}
\section{\sc Conference Publications}

%\subsection{\sc Conferences}
\begin{enumerate}[label={[C\arabic*]}]
\item Nima Dehmamy, Albert-László Barabási, \underline{Rose Yu}.  "Understanding the Representation Power of Graph Neural Networks in Learning Graph Topology" To appear in \textit{Proceeding of Advances in Neural Information Processing Systems} (NeurIPS), 2019
 
 
\item  Yukai Liu, \underline{Rose Yu}, Stephan Zheng, Eric Zhan, Yisong Yue. "NAOMI: Non-Autoregressive Multiresolution Sequence Imputation" To appear in \textit{Proceeding of Advances in Neural Information Processing Systems} (NeurIPS), 2019


\item Guanya Shi, Xichen Shi, Michael O'Connell, \underline{Rose Yu}, Kamyar Azizzadenesheli, Anima Anandkumar, Yisong Yue, Soon-Jo Chung
       "Neural Lander: Stable Drone Landing Control using Learned Dynamics" In \textit{Proceedings  of International Conference on Robotics and Automation} (ICRA), 2019

\item 	Yaguang Li,  \underline{Rose Yu}, Cyrus Shahabi, Yan Liu
	"Diffusion Convolutional Recurrent Neural Network: Data-Driven Traffic Forecasting" In \textit{Proceedings  of  International Conference on Learning Representations
	}(ICLR), 2018 
	
\item  \underline{Rose Yu}, Guangyu Li, Yan Liu. "Tensor regression meets Gaussian Processes." In \textit{Proceedings  of  International Conference on Artificial Intelligence and Statistics } (AISTATS), 2018 

\item \underline{Rose Yu}, Yaguang Li, Ugur Demiryurek, Cyrus Shahabi, Yan Liu. "Deep Learning: A Generic Approach for Extreme Condition Traffic Forecasting." In \textit{Proceedings  of the Seventeenth SIAM International Conference on Data Mining }(SDM), 2017

\item \underline{Rose Yu}, Yan Liu. "Learning from Multiway Data: Simple and Efficient Tensor Regression." In \textit{Proceedings  of the 33th International Conference on Machine Learning }(ICML),   2016

\item Dingxiong Deng, Cyrus Shahabi, Ugur Demiryurek, Linhong Zhu,  \underline{Rose Yu}, Yan Liu, 
"Latent Space Model for Road Networks to Predict Time-Varying Traffic", In \textit{Proceeding of ACM SIGKDD Conference on Knowledge Discovery and Data Mining } (KDD), 2016


\item \underline{Rose Yu}, Andrew Gelfand, Suju Rajan, Cyrus Shahabi, Yan Liu. "Geographic Segmentation via Latent Poisson Factor Model." in \textit{ACM International Conference on Web Search and Data Mining} (WSDM), 2016 

\item \underline{Rose Yu}, Dehua Cheng, Yan Liu. "Accelerated Online Low Rank Tensor Learning for Multivariate Spatiotemporal Streams." In \textit{Proceedings  of the 32th International Conference on Machine Learning} (ICML), 2015

\item \underline{Rose Yu}, Mohammad Taha Bahadori, Yan Liu. "Fast Multivariate Spatio-temporal Analysis via Low Rank Tensor Learning." In \textit{Proceeding of Advances in Neural Information Processing Systems} (NIPS), 2014 \textbf{Spotlight}

\item \underline{Rose Yu}, Xinran He, Yan Liu. "GLAD: Group Anomaly Detection in Social Media Analysis." In \textit{Proceeding of ACM SIGKDD Conference on Knowledge Discovery and Data Mining} (KDD),2014

\item Cuixia Gao, Naiyan Wang,\underline{Qi Yu}, Zhihua Zhang. "A Feasible Nonconvex Relaxation Approach to Feature Selection." In \textit{Proceeding of 24th AAAI conference on Artificial Intelligence} (AAAI), 2011 

\item  \underline{Qi Yu}, Zhihao Ding, Rong Rong, Wang Donghui, Zhengyue Zhang. "Dark Pixel Detection: A Novel Single Image Dehaze Approach". In \textit{Proceeding of 27th Image and Vision Computing New Zealand }(IVCNZ), 2011  
\end{enumerate}

 
\section{\sc Journal Publications}
\begin{enumerate}[label={[J\arabic*]}]
\item \underline{Rose Yu},  Yan Liu.  "Spatio-Temporal Analysis of Social Media Data"  In \textit{Encyclopedia of GIS}, 2016

\item \underline{Rose Yu}, Huida Qiu, Zhen Wen, Ching-Yung Liu,  Yan Liu. "A Survey on Social Media Analysis  Anomaly Detection" In \textit{ACM KDD Exploration},  2016

\item \underline{Rose Yu}, Xinran He, Yan Liu. "GLAD: Group Anomaly Detection in Social Media Analysis - Extended Abstract." In \textit{}ACM Transactions on Knowledge Discovery in Data  (TKDD), 2015
\end{enumerate}

\section{\sc Selected
Workshop
Papers
(Unrefereed) }
\begin{enumerate}[label={[W\arabic*]}]
\item Rui Wang, Adrian Albert, Karthik Kashinath, Mustafa Mustafa, \underline{Rose Yu}. "Towards physics informed deep learning for spatiotemporal modeling of turbulence flow". \textbf{Oral Presentation} at \textit{Advances in Neural Information Processing Systems} (NeurIPS), Machine Learning for Physical Sciences  workshop, 2019

\item Clara De Paolis, Saeed Amizadeh, \underline{Rose Yu}.  "A Neural Framework for Learning DAG to DAG Translation ". In  \textit{Advances in Neural Information Processing Systems} (NeurIPS), relational representation learning workshop, 2018

\item \underline{Rose Yu}, Stephan Zheng, Anima Anandkumar, Yisong Yue. "Long-term forecasting using Tensor-Train RNN". \textbf{Best Paper Award}  in \textit{Advances in Neural Information Processing Systems} (NIPS), time series workshop, 2017


\item Yaguang Li, \underline{Rose Yu}, Cyrus Shahabi, Yan Liu. "Diffusion Convolutional Recurrent Neural Network: Data-Driven Traffic Forecasting". \textbf{Oral Presentation} at \textit{Advances in Neural Information Processing Systems} (NIPS), time series workshop, 2017


\item \underline{Rose Yu}, Stephan Zheng. "Learning Chaotic Dynamics with Tensor RNN". In  \textit{International Conference on Machine Learning} (ICML), Deep structured prediction workshop, 2017

\item \underline{Rose Yu},  Paroma Varma, Dan Iter, Chris De Sa, Christopher Re,  "Socratic Learning".  In \textit{Advances in Neural Information Processing Systems}  (NIPS) future of interactive machine learning workshop, 2016


\item Rose Yu, Yan Liu. "Simple and Efficient Tensor Regression for Spatio-Temporal Forecasting." Poster accepted to \textit{International Workshop on Climate Informatics workshop}(CI), 2016

\item Rose Yu, Dehua Cheng, Yan Liu. "Accelerated Online Low-Rank Tensor Learning for Multi-model Ensemble." Poster accepted to \textit{International Workshop on Climate Informatics workshop} (CI), 2015

\item Mohammad Taha Bahadori, Rose Yu, Yan Liu. "Fast Cokriging via Low Rank Tensor Learning." Poster accepted to \textit{International Workshop on Climate Informatics workshop} (CI), 2014
\end{enumerate}




\end{resume}
\end{document}




